Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-06-18 tex/paper1/paper1.tex
adding in effective number of pixels table

\section{Fitting models to the \mFps}\label{sec:app:ind}

In order to perform the fit, the noise in the \mFps\ must be
estimated.  To do that, the power distributions of Section
\ref{sec:anal} are considered.  The Fourier power at a given pixel is
not independent of the Fourier power at another pixel.  This is
because neighbouring pixels are highly likely to be physically
connected to each other, and so time-series in neighboring pixels are
likely to be strongly correlated (assuming that the background
structure exists over at least two pixels).  Also, the point spread
function of AIA spreads emission in one pixel over on to its
neighbors.  Secondly, the distributions are only approximately normal.

@@

\subsection{Model fitting and selection}

The \mFpa\ are assumed to be normally distributed with a width given by
$\sigma_{mean}$ as calculated above.
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.
The frequency $\nu$ is defined as $f/f_{0}$ where $f$ is the FFT
frequency in Hz, and $f_{0}$ is the lowest non-zero FFT frequency
defined by the data (Section \ref{sec:obs}).  A five step fitting
process is used to fit Models 1 and 2 to the data.  Maximum likelihood
estimates are found using scipy's maximum likelihood estimators

>>>>

\section{Fitting models to the \mFps}\label{sec:app:ind}
In order to perform the fit, the noise in the \mFps\ must be
estimated.  To do that, the power distributions of Section
\ref{sec:anal} are considered.  The Fourier power at a given pixel is
not independent of the Fourier power at another pixel.  This is
because neighbouring pixels are highly likely to be physically
connected to each other, and so time-series in neighboring pixels are
likely to be strongly correlated (assuming that the background
structure exists over at least two pixels).  Also, the point spread
function of AIA spreads emission in one pixel over on to its
neighbors.  Secondly, the distributions are only approximately normal.

@@

\begin{deluxetable}{cc}
\tabletypesize{\scriptsize}
\tablecaption{Number of pixels and effectively independent pixels as a function of region and waveband, as calculated following the procedure of Section \ref{sec:app:ind}. \label{tab:neff}}
\tablewidth{0pt}
\tablehead{
\colhead{Region} &
\colhead{$N_{pixel}$} &
\colhead{Waveband} &
\colhead{$N_{eff}$} &
}
\startdata
loop footpoints & ??? & 171\AA & ??? \\
                & ??? & 193\AA & ??? \\
moss            & ??? & 171\AA & ??? \\
                & ??? & 193\AA & ??? \\
quiet Sun       & ??? & 171\AA & ??? \\
                & ??? & 193\AA & ??? \\
sunspot         & ??? & 171\AA & ??? \\
                & ??? & 193\AA & ??? \\
\enddata
\end{deluxetable}

\subsection{Model fitting and selection}
The \mFpa\ are assumed to be normally distributed with a width given by
$\sigma_{mean}$ as calculated above.
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.
The frequency $\nu$ is defined as $f/f_{0}$ where $f$ is the FFT
frequency in Hz, and $f_{0}$ is the lowest non-zero FFT frequency
defined by the data (Section \ref{sec:obs}).  A five step fitting
process is used to fit Models 1 and 2 to the data.  Maximum likelihood
estimates are found using scipy's maximum likelihood estimators
